---
title: "Thomas Lieb's CV"
author: Thomas Lieb
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{=html}
<!--
TODO
* get sutitle to Gsheet
* get formerly to Gsheet + CSS to .CSS file
* identify and define process for tailor CV for specific applications
* version code?
  * that way tailored CVs could relate to a specific CV
* ?find a picture: QR to Linkedin

# Tailoring CV

Ideas
* copy & adjust spreadsheet and run script by adjusting spreadsheet link
* if code needs to be adjusted, could be done via a branch or copy of code saved along with CV
-->
```


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
offline <- T
if (!offline) {
  CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1KcTSyanKHQ1jGnwVd6AxMcb3zXLvt-2RKzsPOfmI5Cw/edit#gid=917338460",  
  pdf_mode = params$pdf_mode,
  sheet_is_publicly_readable = FALSE
  )
  saveRDS(CV, "CV.RDS")
} else {
  CV <- readRDS("CV.RDS")
}
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r generate_qr_code, include=FALSE}
if (FALSE) {
  require(qrcode)
  link <- "https://www.linkedin.com/in/thomas-lieb-158576a0/"
  qr <- qr_code(link)
  generate_svg(qr, "frame.svg", background = "#f2f2f1")
}
```


<!-- Swap image with your preferred logo -->
<center>
[![logo](frame.svg){width=75%}](https://www.linkedin.com/in/thomas-lieb-158576a0/)
</center>

```{r}
if(params$pdf_mode){
  cat("View an online version of my CV at *https://my.cv.pdf/tbd*")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://my.cv.pdf/tbd)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

Attributes {#attributes}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skills_text(category_filter = "attributes")
```

Main Tech Skills {#main_tech_skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars(bar_color = "#274b9f")
```

Other Tech Skills {#other_tech_skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skills_text(category_filter = "other_tech")
```


Languages {#languages}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skills_table()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available [on github.com/rietho/cv](https://github.com/rietho/cv).

Last updated on `r Sys.Date()`.


# Main

## Thomas Lieb {#title}

```{=html}
<p style="font-size:10px; color:#a8a7a7; margin-top: -5px;">
formerly: Thomas Riebenbauer
</p>
````

```{r}
CV %<>% print_subtitle()
```

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

## Industry Experience {data-icon="suitcase"}

```{=html}
<!--!
::: aside
```{r}
CV %<>% print_text_block('industy_experience_aside')
```
:::
-->
```

```{r}
CV %<>% print_section('industry_positions')
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{=html}
<!--!
::: aside
```{r}
CV %<>% print_text_block('education_aside')
```
:::
-->
```

```{r}
glue_template <- "
### {title}

{institution}

{loc}

{timeline}

:::concise
{description_bullets}
:::
\n\n\n"
CV %<>% print_section('education', glue_template = glue_template)
```

```{=html}
<!-- These breaks just force a new page so section doesnt get cut off 
<br>
<br>
<br>
-->
```
